### 2018-10-12 Manuscript/Manuscript.tex
Updates from ShareLaTeX

\begin{figure}[h!]
\begin{center}
	\includegraphics[width=0.65\textwidth]{Manuscript/Figures/LIP_Preservation.pdf}
	\caption{\textbf{Monte Carlo null hypothesis test
Panel A) total LIP
Panel B) LIP in the tropics
Panel C) continental fraction in the tropics
Panel D) sutures(?)}}
	\label{fig:LIP_correlation}
\end{center}
\end{figure}

>>>>

\begin{figure}[h!]
\begin{center}
	\includegraphics[width=0.85\textwidth]{Manuscript/Figures/overlap_correlation.pdf}
	\caption{\textbf{The overlap and correlation values for various LIP post-emplacement scenarios are shown with circles. These values are compared to histograms that are range of values that arise when comparing the LIP area record to glacial intervals that have been shifted randomly in time 100,000 times. The only scenario for which there is a positive correlation coefficient related to ice extent and LIP area is that of a relatively slow decay rate (d2) and complete burial of LIPs associated with rifting (b2). This positive correlation is weak (\textit{r}=0.10) and is not significant as randomly timed glacial intervals correlate better than the record 28$\%$ of the time. With an associated p-value of 0.28, the null hypothesis that glacial intervals not related to LIP area in the tropics cannot be rejected.}}
	\label{fig:LIP_correlation}
\end{center}
\end{figure}
